What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-05 thesis/proposal_draft.Rmd
update thurs 2
added plots of time series in appendix

>>>>

For testing the proof of concept, a simple web application for viewing average hourly counts for a given month (for a given year) on a map was developed. 
```{r, fig.align = 'center', echo = FALSE, out.width = "66%"}
include_graphics("../img/ped_vis_melb_me.png")
```

### Limitations

#### Model  
The model itself is currently limited to being treating the data as static panel data. A major reason for this is the nature of the data, where the patterns from year to year do not change.

#### Visualisation

### Research Plan
- Imputation that incorporates time and space
- Predicitive model for each sensor
- Visual methods for space-time counts
- Shiny app - interface design, computation
- dynamic
